### 2024-02-19 paper_sisc_first_revision/frog_tau_batches.tex
added frog convergence plots to paper and wrote caption

\begin{document}
	\begin{tikzpicture}[baseline]%, trim axis right]
		\begin{axis}[width=0.49\linewidth, height=0.5\linewidth,
		xmode=log,
		ymode=log,
		ymin=1e-4,
		ymax=1e0,
%		xmax=1000,
		axis x line*=bottom,
		axis y line*=left,
%		xtick={0, 200, 400, 600,800,1000},
		xlabel={\#batches},
%		ylabel={$\|\boldsymbol{\Phi} - \widetilde{\boldsymbol{\Phi}}\|_\text{Fro} / \|\boldsymbol{\Phi}\|_\text{Fro}$},
		title={PSF convergence (batches)},
%		legend style={at={(1.2,1)},anchor=north east,draw=none},
%		legend pos=south west,
%		legend style={font=\small}
		]
%			\addlegendentry{$\tau=2.0$}
			\addplot[black, line width=0.5mm] table {frog_convergence_batches_tau2.0.dat};
%			\addlegendentry{$\tau=2.5$}
			\addplot[blue, line width=0.5mm] table {frog_convergence_batches_tau2.5.dat};
%			\addlegendentry{$\tau=3.0$}
			\addplot[cyan, line width=0.5mm] table {frog_convergence_batches_tau3.0.dat};
%			\addlegendentry{$\tau=3.5$}
			\addplot[purple, line width=0.5mm] table {frog_convergence_batches_tau3.5.dat};
%			\addlegendentry{$\tau=4.0$}
			\addplot[red, line width=0.5mm] table {frog_convergence_batches_tau4.0.dat};
		\end{axis}
	\end{tikzpicture}
\end{document}

>>>>

\begin{document}
	\begin{tikzpicture}[baseline]%, trim axis right]
		\begin{axis}[width=0.49\linewidth, height=0.5\linewidth,
		xmode=log,
		ymode=log,
		ymin=1e-4,
		ymax=1e0,
%		xmax=1000,
		axis x line*=bottom,
		axis y line*=left,
%		xtick={0, 200, 400, 600,800,1000},
		xlabel={\#batches},
%		ylabel={$\|\boldsymbol{\Phi} - \widetilde{\boldsymbol{\Phi}}\|_\text{Fro} / \|\boldsymbol{\Phi}\|_\text{Fro}$},
		title={PSF convergence (batches)},
%		legend style={at={(1.2,1)},anchor=north east,draw=none},
%		legend pos=south west,
%		legend style={font=\small}
		]
%			\addlegendentry{$\tau=2.0$}
			\addplot[olive, line width=0.5mm] table {frog_convergence_batches_tau2.0.dat};
%			\addlegendentry{$\tau=2.5$}
			\addplot[blue, line width=0.5mm] table {frog_convergence_batches_tau2.5.dat};
%			\addlegendentry{$\tau=3.0$}
			\addplot[cyan, line width=0.5mm] table {frog_convergence_batches_tau3.0.dat};
%			\addlegendentry{$\tau=3.5$}
			\addplot[black, line width=0.5mm] table {frog_convergence_batches_tau3.5.dat};
%			\addlegendentry{$\tau=4.0$}
			\addplot[red, line width=0.5mm] table {frog_convergence_batches_tau4.0.dat};
			\addplot[dashed, color=gray, line width=0.5mm] table {frog_convergence_rate_batches.dat};
		\end{axis}
	\end{tikzpicture}
\end{document}

### 2024-02-19 paper_sisc_first_revision/localpsf.tex
added frog convergence plots to paper and wrote caption

In Table~\ref{tab:frog_psf_vs_hodlr_vs_glr} we compare the
computational cost to approximate the blur kernel from
Equation~\eqref{eq:frog_kernel} using the proposed PSF method, the
randomized HODLR (hierarchical off diagonal low rank)
method~\cite{Martinsson16,HartlandEtAl23}, and GLR (global low rank)
approximation using randomized SVD~\cite{HalkoMartinssonTropp11}. For
these results we vary the quantity $L$ to scale the width of the
impulse responses and hence the rank of the operator. For each case,
we calculate the relative error in the approximation of the kernel
measured in the Frobenius norm, $||\boldsymbol{\Phi} -
\widetilde{\boldsymbol{\Phi}}||_\text{Fro} /
||\boldsymbol{\Phi}||_\text{Fro}$ and show the number of operator
applications required to achieve 20\%, 10\%, and 5\% relative error by
each method. The results reveal that superior performance of the PSF
method as compared to the HODLR and GLR methods for all cases. We note
that as we increase the rank and decrease the error tolerance, the
performance of the the HODLR and GLR methods deteriorates.

@@

>>>>

In Table~\ref{tab:frog_psf_vs_hodlr_vs_glr} we compare the
computational cost to approximate the blur kernel from
Equation~\eqref{eq:frog_kernel} using the proposed PSF method, the
randomized HODLR (hierarchical off diagonal low rank)
method~\cite{Martinsson16,Hartland_2023}, and GLR (global low rank)
approximation using randomized SVD~\cite{HalkoMartinssonTropp11}. For
these results we vary the quantity $L$ to scale the width of the
impulse responses and hence the rank of the operator. For each case,
we calculate the relative error in the approximation of the kernel
measured in the Frobenius norm, $||\boldsymbol{\Phi} -
\widetilde{\boldsymbol{\Phi}}||_\text{Fro} /
||\boldsymbol{\Phi}||_\text{Fro}$ and show the number of operator
applications required to achieve 20\%, 10\%, and 5\% relative error by
each method. The results reveal that superior performance of the PSF
method as compared to the HODLR and GLR methods for all cases. We note
that as we increase the rank and decrease the error tolerance, the
performance of the the HODLR and GLR methods deteriorates.

@@

\begin{figure}
	\begin{subfigure}{0.52\textwidth}
		\begin{center}
			\includegraphics[scale=1.0]{frog_tau_impulses.pdf}
		\end{center}
	\end{subfigure}
	\begin{subfigure}{0.47\textwidth}
		\begin{center}
			\includegraphics[scale=1.0]{frog_tau_batches.pdf}
		\end{center}
	\end{subfigure}
	\caption{Relative error in the PSF approximation of the kernel, $||\boldsymbol{\Phi} - \widetilde{\boldsymbol{\Phi}}||_\text{Fro}/||\boldsymbol{\Phi}||_\text{Fro}$, for different ellipsoid size parameters, $\tau$. Left: Relative error vs. the total number of impulse responses used in the approximation. Right: Relative error vs. the number of impulse response batches. The dashed gray lines show linear convergence rates, i.e., $\text{constant} \times \left(\# \text{impulse responses}\right)^{-1}$ on the left, and  $\text{constant} \times \left(\# \text{batches}\right)^{-1}$ on the right.}
	\label{fig:PSF_tau_convergence}
\end{figure}
